Hydra battles in Coq

### 2020-10-20 doc/hydras.tex
new tactics for navigating in the hydra
last push before move

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}). We use an experimental set of tactics for specifying place where the interaction between Hercules and the hydra holds.

@@

\begin{Coqsrc}
Example R2_example:  R2 4 Hy' Hy''.
Proof.
    (** move to 2nd sub-hydra (0-based indices) *) R2_up 1. 
    (** move to first sub-hydra *)  R2_up 0.
    (** we're at distance 2 from the to-be-chopped-off head 
        let's go to the first daughter, then chop-off the leftmost head *)
    last_two 0 0. 
Qed.
\end{Coqsrc}

>>>>

\subsubsection{Example}
Let us prove the transformation of \texttt{Hy'} into \texttt{Hy''} (see Fig.~\vref{fig:Hy3}). We use an experimental set of tactics for specifying the place where the 
interaction between Hercules and the hydra holds.

@@

\begin{Coqsrc}
Example R2_example:  R2 4 Hy' Hy''.
Proof.
    (** move to 2nd sub-hydra (0-based indices) *) R2_up 1. 
    (** move to first sub-hydra *)  R2_up 0.
    (** we're at distance 2 from the to-be-chopped-off head 
        let's go to the first daughter, 
        then chop-off the leftmost head *)  r2_d2  0 0. 
Qed.
\end{Coqsrc}
